Methodology for Assessing the State of the Practice for Domain X

### 2020-03-16 StateOfPractice/Methodology/Methodology.tex
Update Methodology

\title{Methodology for Assessing the State of the Practice for Domain X} 
\author{Spencer Smith}{McMaster University, Canada}{smiths@mcmaster.ca}{}{}
\author{Jacques Carette}{McMaster University, Canada}{carette@mcmaster.ca}{}{}
\author{Olu Owojaiye}{McMaster University, Canada}{owojaiyo@mcmaster.ca}{}{}
\author{Peter Michalski}{McMaster University, Canada}{michap@mcmaster.ca}{}{}
\author{Ao Dong}{McMaster University, Canada}{}{}{}

@@

Measures that can be extracted from on-line repos.

>>>>

\title{Methodology for Assessing the State of the Practice for Domain X} 
\author{Spencer Smith}{McMaster University, Canada}{smiths@mcmaster.ca}{}{}
\author{Jacques Carette}{McMaster University, Canada}{carette@mcmaster.ca}{}{}
\author{Olu Owojaiye}{McMaster University, Canada}{owojaiyo@mcmaster.ca}{}{}
\author{Peter Michalski}{McMaster University, Canada}{michap@mcmaster.ca}{}{}
\author{Ao Dong}{McMaster University, Canada}{donga9@mcmaster.ca}{}{}

@@

\subsection{Raw Data}
Measures that can be extracted from on-line repos.

\ad{Still at brainstorm stage.}
\begin{itemize}
\item number of contributors
\item number of watches
\item number of stars
\item number of forks
\item number of clones
\item number of commits
\item number of total/code/document files
\item lines of total/logical/comment code
\item lines/pages of documents (can pdf be extracted?)
\item number of total/open/closed/merged pull requests
\item number of total/open/closed issues
\item number of total/open/closed issues with assignees
\end{itemize}

\subsection{Processed Data}
Metrics that can be calculated from the raw data.

\ad{Still at brainstorm stage.}
\begin{itemize}
\item percentage of total/open/closed issues with assignees -
Visibility/Transparency
\item lines of new code produced per person-day - Productivity
\item lines/pages of new documents produced per person-day - Productivity
\item number of issues closed per person-day - Productivity
\item percentage of comment lines in the code - maintainability \ad{Not Ao's
qualities}
\end{itemize}

\subsection{Tool Test - HubListener}
\ad{This section is currently a note of unorganized contents. Most parts will be
removed or relocated.}

\hyperlink{https://github.com/pjmc-oliveira/HubListener}{GitHub repo}

Raw:
\begin{itemize}
\item Number of Files
\item Number of Lines
\item Number of Logical Lines
\item Number of Comments
\end{itemize}

Cyclomatic:
\hyperlink{https://www.geeksforgeeks.org/cyclomatic-complexity/}{Intro}
\begin{itemize}
\item Cyclomatic Complexity
\end{itemize}

Halstead:
\hyperlink{https://www.geeksforgeeks.org/software-engineering-halsteads-software-metrics/}{Intro}
\begin{itemize}
\item Halstead Effort
\item Halstead Bugs
\item Halstead Length
\item Halstead Difficulty
\item Halstead Time
\item Halstead Vocabulary
\item Halstead Volume
\end{itemize}

Environment 1:
\begin{itemize}
\item Hardware: laptop
\item OS: Windows 10
\item Node.js version: 12
\item npm version: 6
\item Does it work: No
\item Errors: errors during "npm install" step
\end{itemize}

Environment 2:
\begin{itemize}
\item Hardware: Google Cloud VM
\item OS: Ubuntu 18.04
\item Node.js version: 8
\item npm version: 3
\item Does it work: No
\item Errors: errors during "npm install" step
\end{itemize}

Environment 3:
\begin{itemize}
\item Hardware: Google Cloud VM
\item OS: Ubuntu 18.04
\item Node.js version: 8
\item npm version: 6
\item Does it work: Yes
\item Errors: see following tests
\end{itemize}

Test 1 on environment 3: 
\begin{itemize}
\item Repo: 3D Slicer \hyperlink{https://github.com/Slicer/Slicer}{Github repo}
\item Command line or web app: web app
\item Quick Analyze checked: Yes
\item Time Consumption: 96s
\item Errors/problems: data of total/open/closed issues are missing, data of
Cyclomatic and Halstead metrics are missing.
\end{itemize}

Test 2 on environment 3: 
\begin{itemize}
\item Repo: 3D Slicer \hyperlink{https://github.com/Slicer/Slicer}{Github repo}
\item Command line or web app: web app
\item Quick Analyze checked: No
\item Time Consumption: 4.3hrs
\item Errors/problems: the web app lost response after the analysis
\end{itemize}

Test 3/4 on environment 3: 
\begin{itemize}
\item Ao's repo \hyperlink{https://github.com/Ao99/e-commerce-django}{Github
repo}
\item Command line or web app: web app
\item Quick Analyze checked: Yes/No
\item Time Consumption: 121s/117s
\item Errors/problems: most data are missing
\end{itemize}

Test 5/6 on environment 3: 
\begin{itemize}
\item HubListener
\hyperlink{https://github.com/pjmc-oliveira/HubListener}{Github repo}
\item Command line or web app: web app
\item Quick Analyze checked: Yes/No
\item Time Consumption: 49s/131s
\item Errors/problems: none
\end{itemize}

\ad{This citation needs to be deleted later. It's here because my compiler
doesn't work with 0 citations}
\cite{Emms2019}
